\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

% allow links
\usepackage{hyperref}
% hide links
\hypersetup{hidelinks}


\name{Roman Pit\'ak}
\address{
    +420~776~592~138 \\
    \href{mailto:roman@pitak.net}{roman@pitak.net}
}

\address{
    \href{http://github.com/romanpitak}{\textit{github.com/romanpitak}} \\
    \href{http://pitak.net/blog}{\textit{pitak.net/blog}}
}

\begin{document}

    \begin{rSection}{Work experience}

        \begin{rSubsection}{Kindred group}{02/2013 -- present}{PHP Programmer / Analyst}{Prague}
            \item Implemented distributed data collection service using the~AWS~infrastructure.
            The~servers are written in Literate~CoffeeScript and~the~data is stored in NoSQL database.

            \item Analyzed, designed and~developed the~back~end of web~applications.
            Most were based on the~Nette~framework with MySQL,
            but I~also developed an~e-shop in~Magneto and~collaborated on projects in Symfony~2 with the~Kunstmaan~CMS.

            \item Regularly directly communicated with clients on projects specifics during the~analysis phases.

            \item Designed and~executed the~migration process and~cleanup of over 2000 marketing email templates
            to new email marketing provider.
            Cut the~estimated email deployment times by~80\% by
            creating \href{https://github.com/romanpitak/dotMailer-API-v2-PHP-client}{dotMailer~API client library}
            and~“meta language” in~PHP based on the~HTML object~model.
            This~allowed me to effortlessly create and upload content and~locale variations of the~emails.
            The~library was later recognized by~dotMailer and~added to their list of community~projects.
        \end{rSubsection}

        \begin{rSubsection}{Accenture Services}{03/2011 -- 01/2013}{Application Operation Specialist}{Prague}
            \item Ran and~maintained e-Billing application spread over multiple~servers.
            The~application core was \mbox{an Oracle} database running on~an~HP-UX~machine.
            Data preprocessing and~loading was~controlled by~about four~hundred shell scripts and~binaries.
            Final data population was~provided by 16~MS~Win~2005 servers with~ASP.
            My~duties included: shell~script editing and~development, log~analysis (UNIX, DB),
            installation of~patches and~releases (UNIX, WIN), performance tuning (UNIX)
            and~administration of 9~MS~Win~2005 servers with~ASP.

            \item Volunteered and~created web application providing incident tracking for~our~project.
            This~application was~based on~PHP~5.3 with the~Nette framework, MySQL and~jQuery.
        \end{rSubsection}

        \begin{rSubsection}{Hewlett Packard}{12/2009 -- 08/2010}{1st line UNIX and database remote technical support}{Bratislava}
            \item Identification, undertaking and~solving problems
            in~my~range of~competence and~for~remote
            technical support of~operating systems and~applications.
        \end{rSubsection}

    \end{rSection}

    \begin{rSection}{Programming skills}
        \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
            Advanced & CoffeeScript, PHP~5, shell (bash, ksh~88), /regexp?/, git, sed, awk, SQL, MVC, Nette \\
            Intermediate & AWS, HTML, Jade, JavaScript, XML, Magento \\
            Basic & Sass, jQuery, CSS, Prolog, C/C++, Pascal, Python, LaTeX, Haskell, Oracle~PL/SQL
        \end{tabular}
    \end{rSection}

    \begin{rSection}{Interests}
        hiking (Norway, Belarus), canoeing, woodcraft, handwork, guitar, GNU/Linux \\
        \begin{rSubsection}{}{}{Robotics}{}
            \item In~2004 I~built my~first small robot for~the~Istrobot competition.
            In~2007 I~joined a~team of~fifteen~MFF~UK students
            building a~robot for~the~Eurobot~2008 contest.
            In~2008 I~became head of~hardware department.
            I~coauthored one of the~articles published about our robots
            and~attended the~Eurobot~2009 conference in~France.
        \end{rSubsection}
    \end{rSection}

    \begin{rSection}{Education, certificates, licenses, languages}
        \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
            2006 –- 2009 & Faculty of Mathematics and Physics, Charles University in Prague \\
            2002 –- 2006 & Gymn\'azium Jozefa Gregora Tajovsk\'eho, Bansk\'a Bystrica \\
            & Driving license B \\
            English & proficient (B1) \\
            German & advanced (Higher B2)

        \end{tabular}
    \end{rSection}

\end{document}
